\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-06-03 paper.qmd
Added descriptions for best and poor models

@@

<!--langevitour with best pD model for S-curve-->
::: {#fig-scurve_sc layout-ncol="3" fig-pos="H"}
![](figures/scurve/sc_best_1.png)

@@

Screen shots of the **langevitour** of the S-curve, shows the model-in-data space, a video of the tour animation is available at (<https://youtu.be/4RFNENX_fXk>).
:::

<!--langevitour with bad pD model for S-curve-->
::: {#fig-scurve_sc layout-ncol="3" fig-pos="H"}
![](figures/scurve/sc_bad_1.png)

>>>>

The best model for the S-curve using UMAP (n_neighbors: $15$) was created with $420$ bins. It was determined to be the best model after removing edges with a length greater than $0.134$. The decision was made considering the AIC plot (@fig-mse-aic-scurve), which revealed the occurrence of the minimum at $420$. Additionally, visually, the model accurately captures the geometry of the S-curve by fitting the points everywhere (@fig-scurve_sc_best).

In contrast, a poor model for the S-curve with UMAP was created using only $190$ bins and removing edges with a length greater than $0.3$. This model is inadequate as it has a higher MSE compared to the best model. Visually, the model does not fit the points in some places and mismatches the pattern (@fig-scurve_sc_bad).

@@

<!--langevitour with best pD model for S-curve-->
::: {#fig-scurve_sc_best layout-ncol="3" fig-pos="H"}
![](figures/scurve/sc_best_1.png)

@@

Screen shots of the **langevitour** of the S-curve, shows the model-in-data space, a video of the tour animation is available at (<https://youtu.be/4RFNENX_fXk>). MSE with $0.035$.
:::

<!--langevitour with bad pD model for S-curve-->
::: {#fig-scurve_sc_bad layout-ncol="3" fig-pos="H"}
![](figures/scurve/sc_bad_1.png)

### 2024-06-03 paper.tex
Added descriptions for best and poor models

@@

\caption{\label{fig-scurve_sc}Screen shots of the \textbf{langevitour}
of the S-curve, shows the model-in-data space, a video of the tour
animation is available at (\url{https://youtu.be/4RFNENX_fXk}).}

>>>>

The best model for the S-curve using UMAP (n\_neighbors: \(15\)) was
created with \(420\) bins. It was determined to be the best model after
removing edges with a length greater than \(0.134\). The decision was
made considering the AIC plot (Figure~\ref{fig-mse-aic-scurve}), which
revealed the occurrence of the minimum at \(420\). Additionally,
visually, the model accurately captures the geometry of the S-curve by
fitting the points everywhere (Figure~\ref{fig-scurve_sc_best}).

In contrast, a poor model for the S-curve with UMAP was created using
only \(190\) bins and removing edges with a length greater than \(0.3\).
This model is inadequate as it has a higher MSE compared to the best
model. Visually, the model does not fit the points in some places and
mismatches the pattern (Figure~\ref{fig-scurve_sc_bad}).

@@

\caption{\label{fig-scurve_sc_best}Screen shots of the
\textbf{langevitour} of the S-curve, shows the model-in-data space, a
video of the tour animation is available at
(\url{https://youtu.be/4RFNENX_fXk}). MSE with \(0.035\).}

\begin{minipage}{0.33\linewidth}
\includegraphics{figures/scurve/sc_bad_1.png}\end{minipage}%
%
\begin{minipage}{0.33\linewidth}
\includegraphics{figures/scurve/sc_bad_2.png}\end{minipage}%
%
\begin{minipage}{0.33\linewidth}
\includegraphics{figures/scurve/sc_bad_3.png}\end{minipage}%

\caption{\label{fig-scurve_sc_bad}Screen shots of the
\textbf{langevitour} of the S-curve, shows the model-in-data space, a
video of the tour animation is available at
(\url{https://youtu.be/DHPvhkZ0lUM}). MSE with \(0.090\).}
